Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-29 Article.tex
Update of article + biblio + figure

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible deformation.
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX. Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
However, this technique demands abundant sampling prior to and after the critical deformation which represents the level of strain that leads  the material begins to experience recovery and recrystallization processes, leading to the formation of new grains and a reduction in the average grain size.
Additionally, the cooling phase entails phase changes (according to the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Barnett \eal \cite{barnett2000predicting} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta = f(\sigma)$} \textcolor{red}{Done ! throughout the paper} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

@@

The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done ! throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials like our previous work Tize Mha \eal \cite{TizeMha-2023} and many other works. Then the predictions of $\sigma(\varepsilon)$ are used as inputs for the $\theta(\sigma)$ prediction. Hence, this study offers a replacement of the two smoothing methods with an ANN approach to estimate the critical conditions for DRX.

@@

In this subsection we will determine the critical deformation required to initiate recrystallization.
Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
Their widely-used approach adopts a $3^\text{rd}$ degree polynomial to describe the curve $\theta(\sigma)$, enabling the identification of critical stress and strain ($\sigma_c$ and $\varepsilon_c$) through the second derivative.

@@

It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure \ref{fig:AnnTheta}. The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay !}.
The identical process applies to all 20 stress/strain curves.
These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed} \textcolor{red}{Okay !}}
\label{fig:AnnTheta}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
\caption{Work hardening computation for $1$ strain rate and $5$ temperatures. \OP{Im' not sure that this caption is related to the current figure.} \textcolor{red}{As the results provided by Olivier using an ANN model for each curve are not too much far from those obtained using a single ANN model, I've kept just the Figure directly obtained using a single ANN to illustrate the inflection points. This is for illustrative purposes only, as the critical values used for the rest of the calculation are those based on one ANN model for each curve}.}
\label{fig:nThetaOP}
\end{figure}

@@

As described previously, dynamic recrystallization only occurs when a particular critical condition is met.
The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
Consequently, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those curves.

@@

\OP{Figure 6 has been removed because I think it is useless.} \textcolor{red}{Okay !}
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
%\caption{Work hardening polynomial fiting based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}
%\label{fig:fThetaOP}
%\end{figure}

\begin{table}[h!]
\centering
\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay !}}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\toprule
 & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
 & $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$\\
$0.001$ & $1150$ & $0.124$ & $23.330$ & $0.051$ & $19.116$\\
 & $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$\\
 & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
\hline
 & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
 & $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$\\
$0.01$ & $1150$ & $0.195$ & $38.249$ & $0.086$ & $33.435$\\
 & $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$\\
 & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
\hline
 & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
 & $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$\\
$0.1$ & $1150$ & $0.344$ & $57.774$ & $0.160$ & $51.723$\\
 & $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$\\
 & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
\hline
 & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
 & $1100$ & $0.700$ & $106.61$ & $0.329$ & $94.510$\\
$1$ & $1150$ & $0.700$ & $89.525$ & $0.268$ & $89.067$\\
 & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$\\
 & $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$\\
\bottomrule
\end{tabular}
\label{tab:OPparams}
\end{table}

@@

The DRX process commences at a critical deformation, as previously noted.
The degree of recrystallization can be determined through experimental means.
Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}. \OP{REF ?} \textcolor{red}{Done !}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.% \OP{Is it a copy/paste from a publication? If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned. Please, I will appreciate if you could rearrange it as it would have been made. Thanks !}
}
\label{fig:DRXschema}
\end{figure}
\OP{See the new proposed figure 6} \textcolor{red}{Okay for the new Figure !}

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done !}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively. \OP{Please define steady stress after the peak stress} \textcolor{red}{The steady stress is considered as the minimum one after the peak stress}
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \OP{Who wrote this? REF?} \textcolor{red}{Now references are given before the equation} according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.

@@

\begin{table}[h]
\centering
\caption{JMAK model and Zener-Hollomon dependency parameters.}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$A_c$ & $A_p$& $B_c$& $B_p$& $B_s$& $n_c$ \\
\hline
$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141	$&$10265.8	$&$0.235832	$\\
\toprule
$n_p$ & $m_c$& $m_p$& $m_s$& $k$& $n_k$ \\
\hline
$0.203678	$& $0.188236$&$0.181822$&$-0.19708$&$0.48632$&$3.36531$\\
\bottomrule
\end{tabular}
\label{tab:allparams}
\end{table}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
	\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???} \textcolor{red}{ Done !}}
	\label{fig:nDRX}
\end{figure}
\OP{I think this is not finished yet ?} \textcolor{red}{More explanations have been added bellow}

\textcolor{blue}{The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method. This figure shows the comparisons between the predicted and experimentally measured $X_{drx}$ under the tested temperatures and strain rates. The curves represent the variations of the predicted volume fractions of DRX with plastic strain. It can be easily found that the volume fraction of DRX is significantly dependent on the strain, temperature, as well as strain rate values. The DRX kinetic curves are characterized by S-shape. With the increase of strain, the volume fraction of DRX gradually increases. For a given temperature and strain, the volume fraction of DRX increases with the decrease of strain rate; while for a fixed strain rate and strain, the volume fraction of DRX increases with the increase of temperature. The deviation between the experimental and predicted volume fractions of DRX is not much important indicating that the proposed approach is suitable for predicting DRX for the studied superalloy under the wide tested forming conditions.
The decrease of DRX with the increase of the strain rate can be explained by the fact that the volume fraction
of dynamic recrystallization is sensitive to the forming temperature and strain rate. Especially, under high forming temperature
and low strain rate, the dynamic recrystallization is easy to take
place due to the high grain boundaries mobility. However, due to
the low grain boundaries mobility, the dynamic recrystallization
rate is slow under the low forming temperature and high strain
rate. The correlation observed between experimental and prediction  leads to the validation of the model used in that study and therefore these results will be used subsequently in the simulation section}. \OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension !}

@@

In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate of $0.01~\ps$.
Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
The $5\%$ corresponds to the dead zone, representing the contact area between the sample and die experiencing friction effects.
In contrast, $100\%$ corresponds to the value observed at the center of the sample where deformation is the highest.
The temperature is elevated at the center of the sample, leading to a significant accumulation of energy.
Conversely, at the edges of the sample, a relatively complete recrystallization is observed. This is because the temperature during deformation shifts from the center towards the outer regions of the piece, allowing recrystallization to occur.
Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
\OP{Is it possible to have a table of comparison between the num and exp values of $X_{drx}$?} \textcolor{red}{We didn't evaluate experimentaly the DRX's value if I remember. Maybe in the future We will think to do something like that !}
\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \OP{Please, enhance and finalize this figure} \textcolor{red}{Done !}}
\label{fig:expNumDRX}
\end{figure}

>>>>

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation.
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Barnett \eal \cite{barnett2000predicting}\OP{M.J. suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation. You could find review papers about this.)} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

@@

The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials like our previous work Tize Mha \eal \cite{TizeMha-2023} and many other works.
Then the predictions of $\sigma(\varepsilon)$ are used as inputs for the $\theta(\sigma)$ prediction.
Hence, this study offers a replacement of the two smoothing methods with an ANN approach to estimate the critical conditions for DRX.

@@

In this subsection we will determine the critical deformation required to initiate recrystallization.
Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow} were the pioneers in investigating this phenomenon.
Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, jonas2003critical} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
Their widely-used approach adopts a $3^\text{rd}$ degree polynomial to describe the curve $\theta(\sigma)$, enabling the identification of critical stress and strain ($\sigma_c$ and $\varepsilon_c$) through the second derivative.

@@

It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure \ref{fig:AnnTheta}.
The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
The identical process applies to all 20 stress/strain curves.
These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
\label{fig:AnnTheta}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
\caption{Work hardening computation for one strain rate and five temperatures.}
\label{fig:nThetaOP}
\end{figure}

@@

As described previously, dynamic recrystallization only occurs when a particular critical condition is met.
The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
Consequently, the Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those curves.

@@

\begin{table}[h!]
\centering
\caption{Critical conditions based on the proposed approach.}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
\toprule
 & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
 & $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$\\
$0.001$ & $1150$ & $0.124$ & $23.330$ & $0.051$ & $19.116$\\
 & $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$\\
 & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
\hline
 & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
 & $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$\\
$0.01$ & $1150$ & $0.195$ & $38.249$ & $0.086$ & $33.435$\\
 & $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$\\
 & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
\hline
 & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
 & $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$\\
$0.1$ & $1150$ & $0.344$ & $57.774$ & $0.160$ & $51.723$\\
 & $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$\\
 & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
\hline
 & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
 & $1100$ & $0.700$ & $106.61$ & $0.329$ & $94.510$\\
$1$ & $1150$ & $0.700$ & $89.525$ & $0.268$ & $89.067$\\
 & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$\\
 & $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$\\
\bottomrule
\end{tabular}
\label{tab:OPparams}
\end{table}

@@

The DRX process commences at a critical deformation, as previously noted.
The degree of recrystallization can be determined through experimental means.
Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.}
\label{fig:DRXschema}
\end{figure}

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
The steady stress is considered as the minimum one after the peak stress.
It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
\begin{equation}
\begin{cases}
\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
\end{cases}
\label{eq:paramsZ}
\end{equation}
With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.

@@

\begin{table}[h]
\centering
\caption{JMAK model and Zener-Hollomon dependency parameters.}\vspace{-1mm}
\begin{tabular}{cccccc}
\toprule
$A_c$ & $A_p$& $B_c$& $B_p$& $B_s$& $n_c$ \\
\hline
$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141	$&$10265.8	$&$0.235832	$\\
\toprule
$n_p$ & $m_c$& $m_p$& $m_s$& $k$& $n_k$ \\
\hline
$0.203678	$& $0.188236$&$0.181822$&$-0.19708$&$0.48632$&$3.36531$\\
\bottomrule
\end{tabular}
\label{tab:allparams}
\end{table}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
	\caption{DRX experimental data (dots) and JMAK model based prediction (plain lines).}
	\label{fig:nDRX}
\end{figure}

The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX}.
The figure compares the experimentally measured $X_{drx}$ with the predicted values under the tested strain rates and temperatures. \OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data. Also check that the color of the dots is on in Figure 7.}
The curves illustrate the changes in predicted volume fractions of DRX with plastic strain.
It is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
At a constant temperature and strain, the DRX volume fraction increases with decreasing strain rate.
Conversely, at a fixed strain rate and strain, the DRX volume fraction increases with rising temperature.
The difference between the predicted and experimental volume fractions of DRX is insignificant, confirming the suitability of the proposed approach for DRX prediction in the studied superalloy under various forming conditions.
The reduction of DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to forming temperature and strain rate.
Dynamic recrystallization is prone to occur at high forming temperatures and low strain rates due to increased grain boundary mobility.
However, because of the limited mobility of grain boundaries, the rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
The validation of the model used in the study, as evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation section.

@@

In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate of $0.01~\ps$.
Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
The $5\%$ corresponds to the dead zone, representing the contact area between the sample and die experiencing friction effects.
In contrast, $100\%$ corresponds to the value observed at the center of the sample where deformation is the highest.
The temperature is elevated at the center of the sample, leading to a significant accumulation of energy.
Conversely, at the edges of the sample, a relatively complete recrystallization is observed.
This is because the temperature during deformation shifts from the center towards the outer regions of the piece, allowing recrystallization to occur.
Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.

\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$.}
\label{fig:expNumDRX}
\end{figure}
